---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hfsubsetR

<!-- badges: start -->
[![R CMD Check](https://github.com/lynker-spatial/hfsubsetR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lynker-spatial/hfsubsetR/actions/workflows/R-CMD-check.yaml) [![Dependencies](https://img.shields.io/badge/dependencies-6/70-orange?style=flat)](#)
<!-- badges: end -->

The goal of `hfsubsetR` is to extract hydrofabric subsets from cloud or local archives built in `lynker-spatial`.

## Installation

You can install the development version of `hfsubsetR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lynker-spatial/hfsubsetR")
```

## Remote Access

This is a basic example which shows you how to solve a common problem:

```{r remote}
## basic example code
```

## Local

This is a basic example which shows you how to solve a common problem:

```{r local}
## basic example code
```

## Hydrolocation Extraction

This is a basic example which shows you how to solve a common problem:

```{r hydrolocation}
## basic example code
```